---
title: "Jacob McPherson, PharmD"
author: "Jacob McPherson"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
url: https://jacobkmcpherson.netlify.app/
description: For the betterment of man-kind
link-citations: yes
github-repo: jacobkmcpherson/jacobkmcpherson
---

# About

This is a *sample* book written in **Markdown**. You can use anything that Pandoc's Markdown supports; for example, a math equation $a^2 + b^2 = c^2$.

## Usage

Each **bookdown** chapter is an .Rmd file, and each .Rmd file can contain one (and only one) chapter. A chapter *must* start with a first-level heading: `# A good chapter`, and can contain one (and only one) first-level heading.

Use second-level and higher headings within chapters like: `## A short section` or `### An even shorter section`.

The `index.Rmd` file is required, and is also your first book chapter. It will be the homepage when you render the book.

## Render book

You can render the HTML version of this example book without changing anything:

1.  Find the **Build** pane in the RStudio IDE, and

2.  Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

## Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

# Automated Rendering

## Enabling GitHub Pages

To enable GitHub Pages for your repository, follow these steps:

1. Go to the repository settings on GitHub.
2. Scroll down to the "GitHub Pages" section.
3. Select the branch you want to publish from (e.g., `main`) and the folder (e.g., `/docs`).
4. Click "Save" to enable GitHub Pages.

## Creating a GitHub Actions Workflow

To automate the rendering of your bookdown project using GitHub Actions, follow these steps:

1. Create a new directory called `.github/workflows` in the root of your repository if it doesn't already exist.
2. Inside the `.github/workflows` directory, create a new file called `main.yml`.
3. Add the following content to the `main.yml` file:

```yaml
name: Render Bookdown

on:
  push:
    branches:
      - main
  pull_request:
    branches:
      - main

jobs:
  build:
    runs-on: ubuntu-latest

    steps:
    - name: Checkout repository
      uses: actions/checkout@v2

    - name: Set up R
      uses: r-lib/actions/setup-r@v2

    - name: Install dependencies
      run: |
        Rscript -e 'install.packages(c("bookdown", "knitr", "rmarkdown"))'

    - name: Render book
      run: |
        Rscript -e 'bookdown::render_book()'

    - name: Deploy to GitHub Pages
      uses: peaceiris/actions-gh-pages@v3
      with:
        github_token: ${{ secrets.GITHUB_TOKEN }}
        publish_dir: ./_book
```
